### 2018-03-06 tex/paper.tex
Add timeout alternative continuation to CommitCash

\begin{haskellcode}
data Contract =
   Null |
   CommitCash IdentCC Person Cash Timeout Timeout Contract |  
   RedeemCC IdentCC Contract |
   Pay IdentPay Person Person Cash Timeout Contract |  
   Both Contract Contract |
   Choice Observation Contract Contract |
   When Observation Timeout Contract Contract   
   \end{haskellcode}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is part of the infrastructure of this language to record the values of *observables* that are used. However, we have chosen no to make it part of the language itself.}

@@

\item \haskellinline{CommitCash idCC p n t1 t2 k}  For this contract to make progress,\begin{itemize}
\item either before the timeout \haskellinline{t1} the user \haskellinline{p} makes a cash commitment of value \haskellinline{n} and timeout \haskellinline{t2}  with the identifier \haskellinline{idCC} , 
\item
or the timeout \haskellinline{t1} is exceed.
\end{itemize} 
In the first case, a \haskellinline{SuccessfulCommit} action is generated; in both cases, the contract then continues as \haskellinline{k}. While neither case holds the contract is quiescent, waiting for the cash to be committed.

>>>>

\begin{haskellcode}
data Contract =
   Null |
   CommitCash IdentCC Person Cash Timeout Timeout Contract Contract |  
   RedeemCC IdentCC Contract |
   Pay IdentPay Person Person Cash Timeout Contract |  
   Both Contract Contract |
   Choice Observation Contract Contract |
   When Observation Timeout Contract Contract   
   \end{haskellcode}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is part of the infrastructure of this language to record the values of *observables* that are used. However, we have chosen no to make it part of the language itself.}

@@

\item \haskellinline{CommitCash idCC p n t1 t2 k1 k2}  For this contract to make progress,\begin{itemize}
\item either before the timeout \haskellinline{t1} the user \haskellinline{p} makes a cash commitment of value \haskellinline{n} and timeout \haskellinline{t2}  with the identifier \haskellinline{idCC} , 
\item
or the timeout \haskellinline{t1} is exceed.
\end{itemize} 
In the first case, a \haskellinline{SuccessfulCommit} action is generated and the contract continues as 
\haskellinline{k1}; in the second case no action is generated and the contract continues as 
\haskellinline{k2}. While neither case holds the contract is quiescent, waiting for the cash to be committed.
